%-------------------------
% Resume in Latex
% Author : Chetan Kharel
%------------------------

\input{glyphtounicode}
\pdfgentounicode=1

\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage{tabularx}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Chetan Kharel}}\\
	chetankharel7@email.com $\cdot$ https://chetank.dev $\cdot$ +01 00000000 $\cdot$ https://www.linkedin.com/in/chetan-k-3741a0119/\\
\end{center}


%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{Envless} \hfill Remote\\
\textit{Core Contributor} \hfill Dec 2022 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Built an environment variable editor which supports YAML, JSON and ENV file format.
	\item Automated Node.js CLI app to distribute to major platforms.
	\item Building components with React and Tailwind CSS.
	\item Helping new contributors in the project.
	\item Writing type-safe backend APIs with TRPC and Node.js.
\end{itemize}

\textbf{CoveredPress} \hfill Remote\\
\textit{Software Engineer} \hfill Sep 2021 - Dec 2022\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Implemented Meilisearch for global search feature that increased the performance by 20-30\% and search results are more accurate as compared to direct SQL search query.
	\item Built RESTful APIs with Laravel which includes resource APIs and handling background jobs.
	\item Integrating the UI/UX using React and Next.js.
\end{itemize}

\textbf{Shangrila Microsystem} \hfill Kathmandu, Nepal\\
\textit{Software Engineer} \hfill July 2017 - Aug 2021\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Ported date storage and synchronization system from regular file system to Redis database.
	\item Built a logging system that uses database as the driver and UI to filter and view summary of the database and HTTP request related logs.
	\item Built a generalized charting system for Laravel apps that is used across projects within the company.
	\item Generating complex reports using JsReport and Handlebars.
	\item Wrote a custom script using Powershell to generate Fluent Migration (C\# library) to generate database migration files.
	\item Built UIs using Ext.js (an enterprise JavaScript UI framework) for the ERP systems.
	\item Built UIs using Vue 2 and Vuetify for customer facing Taxpayer dashboard.
\end{itemize}


%==== Skills ====%
\header{Skills}
\begin{tabularx}{\textwidth}{ l X } 
	Software Engineer:  Node.js, TypeScript, React, Vue, Go, PHP, Redis, SQL, Laravel, C\#      \\
	Others:       Git \& Vim, Bash scripting, Linux, AWS S3, AWS EC2  \\
\end{tabularx}
\vspace{2mm}

%==== Projects ====%
\header{Projects}
{\textbf{Pegasus}}\hfill https://github.com/chetannn/pegasus\\
A simple version of zero downtime deployment platform for Laravel apps.\\
\vspace*{2mm}
{\textbf{Ecommerce-Aggregator-Api}}\hfill https://github.com/chetannn/ecommerce-aggregator-api\\
A scrapper with apis that aggregates products from various e-commerce website of Nepal.\\
\vspace*{2mm}
{\textbf{Dami-Yatra-Api}}\hfill https://github.com/chetannn/dami-yatra-api\
A final year project built with Laravel which is a simple platform that connects the tourism adveritsement vendors and customers along with payment integration.\\
\vspace*{2mm}
{\textbf{Dami-Yatra-Frontend}}\hfill https://github.com/chetannn/dami-yatra-api\
Frontend for final year project built with Nuxt 2, Bulma, and Vue.\\
\vspace*{2mm}
\ 
\end{document}
